---
title: "Example 2"
author: "Brian Craft"
date: "April 8, 2017"
output: html_document
---

```{r}
library(knitr)
setwd("~/Documents/Craft-Repo/social_networks/example_2")
read_chunk("example02.R")
knitr::opts_chunk$set(echo = TRUE)
```
## Working with different types of data

### Step 1: Load the necessary libraries and data

```{r C1, results="hide", warning=FALSE, message=FALSE}

```

Loading the Southern Women network (Davis data). GraphML format.

```{r C2}
```

### Step 2: Examine the bipartite network
Verify that it is bipartite.

```{r C3}

```

Plot using bipartite layout (better if rotated)
```{r C4}

```

Look at labels and types

```{r C5}

```

So, FALSE is people

### Step 3: Create projection

Create person-person projection

```{r C6}

```

Plot the projected graph
```{r C7}

```

Plot the distribution of edge weights
```{r C8}

```

### Step 4: Filtered version of the network

Create a new network removing the edges of weight 1 and 2.

```{r C9}

```


Plot the weighted degree distribution of the new network
```{r C10}

```

### Step 5: Ego networks

Extract the ego networks for Laura and Sylvia

```{r C11}

```

Plot side-by-side use layout_as_star
```{r C12}


```

Compare the two ego networks by weighted degree. First create data frame with the right structure.

wdeg, ego
10, Laura
24, Sylvia
34, Laura

```{r C13}

```

Then plotting with ggplot is straightforward.

```{r C14}

```

### Step 6: New example: loading edge and attribute data

Load CSV files for edges and attributes. stringAsFactors is
false because we can't use factors as node attributes.

```{r C15}

```

Convert to a graph from the two data frames. Note that the
names of the vertices in the edge data frame have to match the
first column of the vertices data frame.

```{r C16}
```

Plot

```{r C17}

```
