---
title: "Homework 2 (CSC 495)"
author: "Brian Craft"
date: "Spring 2017"
output: html_document
---

## Working with the Beer Advocate data
### Bipartite networks and ego networks

```{r}
library(knitr)
setwd("~/Documents/Craft-Repo/social_networks/homework_2")

read_chunk("hwk2.R")
knitr::opts_chunk$set(echo = TRUE)
```

### Step 1: Load libraries

```{r C1, results="hide", warning=FALSE, message=FALSE}
```

### Step 2: Load the data _1 pt_

Load a bipartite network built from the "Beer Advocate"
review data. For the purposes of this assignment, I selected
only very active users (> 1000 reviews), chose the beers with the
very top ratings (> 4.5 out of 5) and looked at just "American
IPA" style beers. This gives a network of managable size with
278 nodes (131 beers and 147 users). 

The data is in edgelist and attribute form, so we have to 
shape it into a network first. The two files are

- beer_edges.csv
- beer_attrs.csv

```{r, C2}

```

### Step 3: Use graph.data.frame to convert to graph _1 pt_

```{r, C3}

```

### Step 4: Looking at attributes _1 pt_

List the vertex attributes and note that most attributes are 
for beers. We don't have attributes for users.

Use the ```head``` function to list the first 6 (head) beer 
names (not the numeric IDs)
```{r, C4}

```

### Step 5: Projection _1 pt_

Compute the user-user and beer-beer projections and print
the ```summary``` information for each.

```{r, C5}

```

### Step 6: Fixing the attributes _1 pt_

Remove the irrelevant attributes from the user-user network.
Print the summary at the end. It should show only "name" and
"weight" attributes. Use `delete_vertex_attr`.

```{r, C6}

```

### Step 7: Plot the edge weight distribution _2 pt_

You can use either base plotting or ggplot. Label your plots
appropriately (x and y axes, main title). Make sure that the whole distribution
is included -- set x axis limits correctly.

```{r, C7}

```

### Step 8: Filter out edges of weight < 6 _2 pts_

As is typical with projections of bipartite networks, we'll
filter out the low weight edges of which there are very many.

```{r, C8}

```

### Step 9: Remove singletons (nodes of degree == 0) _1 pt_

Removing edges leaves some nodes disconnected from the network
so we remove them also. Another way to do this would be
calculate the largest (giant) component.

```{r, C9}

```

### Note: _Use the filtered version of the network for the rest of the assignment._

### Step 10: Plot the network _1 pt_

The graph is now simplified enough that it can be visualized. Use the Kamada-Kawai
layout: `layout=layout_with_kk`.

```{r, C10}

```

### Step 11: Weighted degree _2 pt_

Compute a histogram of the weighted degree. (`graph.strength` function)

```{r, C11}

```

### Step 12: Find outliers _2 pt_

Find the names of the two individuals with highest weighted
degree (2 outliers)

```{r, C12}

```
### Step 13: Compute the ego networks _1 pt_

Compute the ego networks for these two users.
```{r, C13}

```

### Step 14: Plot the ego networks side by side _1 pt_
Use par(mfrow=c(1,2)) to get the side-by-side layout. Remember to switch back to the normal layout c(1,1) after.

```{r, C14}

```

### Step 15: Question _3 pts_

In reducing the size of the network through edge and vertex
filtering (steps 8 and 9) so that it is easier to visualize, 
what information about the original user-user network has been
lost? What consequences does this have for our interpretation
of the filtered version of the network?

It's possible that by removing weights less than 6 
many singeltons were created, which was step 8.  Then
in step 9, we remove the singeltons, which may have been
because of step 8.  In conjunction, we lost a lot of information
about less active users, since they are not rating as many items,
which could mean selectivity.  For instance, perhaps many of those 
individuals rated the same selective number of beers because
they are from the same area.  Essentially, we lose information
on how the less engaged users are connected.


